\textbf{Supporting Information:}

### 2020-09-01 Supplementary_material/Supp_Material.tex
Insert table
pfinal edits

\title{\textbf{Supporting Information:}}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\section{Recipient and donor characteristics govern hierarchical
structure in a heterospecific pollen competition network of co-flowering
plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}

\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman,
Romina Rader

@@

\textbf{Table S2.} Numerical values of all the traits measured for each
species.

\textbf{Table S3.} Seed set in percentage for hand cross-pollination,
hand self-pollination, natural selfing and apomixis for all species.

\textbf{Table S4.} Species x species matrix with the significance of
effect ``yes'' or ``no'' of the different donors on the seed set of the
different recipient species.

\textbf{Table S5.} Estimates, standard error, t-value and P-value of the
effect of the different 9 donors on each recipient species.

\textbf{Table S6.} Number of seeds produced with 100\% foreign pollen
treatments for the different recipient species.

\textbf{Table S7.} Phylogenetic signal and significance for all the
different traits

@@

\textbf{Figure S1.} Correlation matrix for all the different traits.

\textbf{Figure S2.} Total amount of pollen found for the different
treatments.

\textbf{Figure S3.} Pollen ratios for the different recipient species.

\textbf{Figure S4.} Pollen ratios for the different recipient species by
family.

\textbf{Figure S5.} Statistical comparison of pollen ratios by family as
pollen donor and recipient.

\textbf{Figure S6.} Violin plot of the reproductive biology of the
species.

Figure S7. Grouped effect sizes by family for each recipient species.

>>>>

\usepackage{setspace}\doublespacing
\usepackage{float}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\captionsetup[figure]{labelformat=empty}
\captionsetup[table]{labelformat=empty} \renewcommand{\figurename}{}

\section{Supporting information:}\label{supporting-information}

\section{Recipient and donor characteristics govern the hierarchical
structure of heterospecific pollen competition
networks}\label{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}

\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman,
Romina Rader

@@

\textbf{Table S2.} Trait measurements for all species.

\textbf{Table S3.} Average number of pollen grains of the recipient and
donor species per stigma with the 50:50 mix CP:HP pollen.

\textbf{Table S4.} Seed:ovule ratio (\%) of the different reproductive
biology treatments.

\textbf{Table S5.} Summary of the effect from the linear models of the
different pollen donors on each recipient species.

\textbf{Table S6.} Estimates, standard error, t-value and \emph{P}-value
of the effect of the different 9 donors on each recipient species.

\textbf{Table S7.} Total number of seeds produced with the 100\% foreign
pollen treatments.

@@

\textbf{Table S9.} Phylogenetic signal and significance for all the
different traits.

\textbf{Figure S1}. Average number of pollen grains of recipient and
donor species per stigma with the 50:50 mix CP:HP pollen.

\textbf{Figure S2}. Average proportion (\%) of conspecific and
heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.

\textbf{Figure S3}. Average proportion (\%) of heterospecific and
conspecific pollen per stigma and family with the 50:50 mix CP:HP
pollen.

\textbf{Figure S4}. Statistical comparison of the percentage of
heterospecific pollen with the 50:50 pollen mix by family.

\textbf{Figure S5}. Unipartite bidirectional network with asymmetrical
effect.

\textbf{Figure S6}. Correlation matrix for all the different traits.

\textbf{Figure S7}. Species reproductive biology.

\textbf{Figure S8}. Grouped effect sizes by family for each recipient
species.

\newpage

\begingroup\fontsize{10}{12}\selectfont

\begin{longtabu} to \linewidth {>{\em}l>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:unnamed-chunk-1}\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.}\\
\toprule
\textbf{Species} & \textbf{Common names} & \textbf{Varieties} & \textbf{Source}\\
\midrule
\endfirsthead
\caption[]{\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds. \textit{(continued)}}\\
\toprule
Species & Common names & Varieties & Source\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\rowcolor{gray!6}  Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
\addlinespace
Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
\addlinespace
Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
\addlinespace
Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
\addlinespace
Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
\addlinespace
Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
\end{longtabu}

\endgroup{}

\begin{landscape}

\begin{table}

\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Average values of the trait measurements for each plant species. Sample sizes are provided on the methods section. Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods. The raw data can be found on the online repository provided within this manuscript.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{6}{8}\selectfont
\begin{tabu} to \linewidth {>{\em}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Pollen size $\mu$m} & \textbf{Pollen grains per anther} & \textbf{Ovule number} & \textbf{Pollen:ovule ratio} & \textbf{Stigma area $\mu$m$^{2}$} & \textbf{Stigma length (mm)} & \textbf{Stigma width (mm)} & \textbf{Style length (mm)} & \textbf{Style width (mm)} & \textbf{Ovary length (mm)} & \textbf{Ovary width (mm)} & \textbf{Selfing rate} & \textbf{SI index}\\
\midrule
\rowcolor{gray!6}  Brassica oleracea & 27.72 & 42033 & 29 & 8696.48 & 0.62 & 0.53 & 0.88 & 2.32 & 0.65 & 5.93 & 1.11 & 0.0 & 0.00\\
\addlinespace
Brassica rapa & 25.35 & 7133 & 26 & 1646.08 & 0.36 & 0.37 & 0.73 & 1.08 & 0.52 & 3.53 & 0.88 & 0.0 & 0.00\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & 32.46 & 30761 & 241 & 765.83 & 1.06 & 0.72 & 1.18 & 3.24 & 1.06 & 3.15 & 5.80 & 0.8 & 0.64\\
\addlinespace
Eruca versicaria & 24.95 & 22151 & 24 & 5537.75 & 0.35 & 0.73 & 0.67 & 6.60 & 0.73 & 4.42 & 0.94 & 0.1 & 0.02\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & 70.10 & 858 & 4 & 1072.50 & 3.26 & 1.43 & 2.25 & 19.44 & 0.45 & 2.38 & 1.42 & 0.6 & 0.75\\
\addlinespace
Ipomoea purpurea & 97.59 & 654 & 6 & 545.00 & 2.27 & 1.24 & 1.88 & 28.23 & 0.58 & 1.06 & 1.57 & 1.0 & 2.74\\
\addlinespace
\rowcolor{gray!6}  Petunia integrifolia & 24.74 & 34657 & 220 & 787.66 & 1.17 & 0.80 & 1.32 & 14.65 & 0.45 & 3.13 & 1.77 & 0.9 & 0.26\\
\addlinespace
Sinapis alba & 33.59 & 3507 & 6 & 3507.00 & 0.55 & 0.63 & 0.91 & 3.62 & 0.77 & 1.98 & 1.07 & 0.7 & 1.12\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & 22.00 & 28915 & 92 & 1885.76 & 0.09 & 0.19 & 0.35 & 6.47 & 0.31 & 1.16 & 1.13 & 0.7 & 0.48\\
\addlinespace
Solanum melongena & 25.18 & 166989 & 1010 & 992.01 & 1.14 & 0.96 & 1.33 & 11.33 & 0.94 & 4.02 & 3.55 & 1.0 & 1.45\\
\bottomrule
\end{tabu}}
\end{table}

\end{landscape}

\newpage

\begin{table}

\caption{\label{tab:unnamed-chunk-3}\textbf{Table S3.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\em}l>{\em}l>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Recipient species} & \textbf{Donor species} & \textbf{Recipient pollen grains} & \textbf{Donor pollen grains}\\
\midrule
\rowcolor{gray!6}  C. annuum & I. purpurea & 258 & 11\\
\addlinespace
E. sativa & I. purpurea & 1308 & 8\\
\addlinespace
\rowcolor{gray!6}  B. oleracea & I. purpurea & 90 & 20\\
\addlinespace
B. rapa & I. purpurea & 193 & 2\\
\addlinespace
\rowcolor{gray!6}  S. melongena & I. aquatica & 64 & 26\\
\addlinespace
P. integrifolia & I. aquatica & 23 & 20\\
\addlinespace
\rowcolor{gray!6}  S. lycopersicum & I. aquatica & 56 & 10\\
\addlinespace
S. alba & I. aquatica & 1617 & 19\\
\addlinespace
\rowcolor{gray!6}  I. purpurea & S. melongena & 138 & 362\\
\addlinespace
S. alba & S. melongena & 3054 & 1096\\
\addlinespace
\rowcolor{gray!6}  E. sativa & P. integrifolia & 621 & 321\\
\addlinespace
B. rapa & S. lycopersicum & 1114 & 246\\
\addlinespace
\rowcolor{gray!6}  I. aquatica & C. annuum & 35 & 85\\
\addlinespace
B. oleracea & C. annuum & 281 & 209\\
\addlinespace
\rowcolor{gray!6}  I. purpurea & E. sativa & 27 & 216\\
\addlinespace
S. melongena & E. sativa & 1837 & 2231\\
\addlinespace
\rowcolor{gray!6}  P. integrifolia & B. oleracea & 332 & 376\\
\addlinespace
I. aquatica & S. alba & 42 & 170\\
\addlinespace
\rowcolor{gray!6}  C. annuum & S. alba & 304 & 450\\
\addlinespace
S. lycopersicum & B. rapa & 164 & 208\\
\bottomrule
\end{tabu}}
\end{table}

\newpage

\begin{table}

\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species. The values provided are the seed:ovule ratios in percentage.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\em}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Hand cross-pollination} & \textbf{Hand self-pollination} & \textbf{Spontaneous selfing} & \textbf{Apomixis}\\
\midrule
\rowcolor{gray!6}  Brassica oleracea & 32.07 & 0.00 & 0.00 & 0\\
\addlinespace
Brassica rapa & 44.97 & 0.00 & 0.00 & 0\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & 80.00 & 56.47 & 19.34 & 0\\
\addlinespace
Eruca sativa & 23.75 & 0.42 & 0.00 & 0\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & 40.00 & 30.00 & 20.00 & 0\\
\addlinespace
Ipomoea purpurea & 31.67 & 86.67 & 31.67 & 0\\
\addlinespace
\rowcolor{gray!6}  Petunia integrifolia & 80.16 & 24.77 & 0.00 & 0\\
\addlinespace
Sinapis alba & 41.67 & 48.33 & 5.00 & 15\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersium & 85.65 & 41.20 & 68.48 & 0\\
\addlinespace
Solanum melongena & 60.48 & 74.87 & 21.56 & 0\\
\bottomrule
\end{tabu}}
\end{table}

\begin{landscape}

\begin{table}

\caption{\label{tab:unnamed-chunk-5}\textbf{Table S5.} Summary of the heterospecific pollen impacts from the linear models on each pollen recipient species. The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control treatment. Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{6}{8}\selectfont
\begin{tabu} to \linewidth {>{\em}l>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright}X>{\raggedright}X}
\toprule
\em{} & \em{Brassica oleracea} & \em{Brassica rapa} & \em{Eruca sativa} & \em{Sinapis alba} & \em{Ipomoea aquatica} & \em{Ipomoea purpurea} & \em{Capsicum annuum} & \em{Petunia integrifolia} & \em{Solanum lycopersicum} & \em{Solanum melongena} & \em{$\%$ of significant effect}\\
\midrule
\rowcolor{gray!6}  B. oleracea &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 100\\
\addlinespace
B. rapa & No &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 88.9\\
\addlinespace
\rowcolor{gray!6}  E. sativa & Yes & No &  & No & Yes & No & No & No & No & No & 22.2\\
\addlinespace
S. alba & No & Yes & No &  & Yes & Yes & Yes & No & No & No & 44.4\\
\addlinespace
\rowcolor{gray!6}  I. aquatica & Yes & Yes & Yes & Yes &  & Yes & Yes & Yes & Yes & Yes & 100\\
\addlinespace
I. purpurea & No & No & Yes & No & No &  & Yes & No & Yes & No & 33.3\\
\addlinespace
\rowcolor{gray!6}  C. annuum & Yes & Yes & No & Yes & No & Yes &  & Yes & Yes1 & Yes & 77.8\\
\addlinespace
P. integrifolia & Yes & No & No & Yes & Yes & Yes & No &  & Yes & Yes & 67.7\\
\addlinespace
\rowcolor{gray!6}  S. lycopersicum & No & Yes & Yes & Yes & Yes & Yes & Yes & Yes &  & Yes & 88.9\\
\addlinespace
S. melongena & No & Yes & Yes & No & Yes & Yes & Yes & No & No &  & 55.6\\
\addlinespace
\rowcolor{gray!6}   &  &  &  &  &  &  &  &  &  &  & $\bar{X}=67.8$\\
\bottomrule
\end{tabu}}
\end{table}

\end{landscape}

\clearpage

\begingroup\fontsize{7}{9}\selectfont

\begin{longtable}[t]{>{\em}lrrrr}
\caption{\label{tab:unnamed-chunk-6}\textbf{Table S6.} Results of the linear models conducted to test the effect of heterospecific pollen with the 50-50 CP-HP pollen treatments. We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept). The first species on the row names are the pollen recipient species and the second species the pollen donor species. Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses.}\\
\toprule
\textbf{ } & \textbf{Estimates} & \textbf{Standard error} & \textbf{t-value} & \textbf{{\textit{P}}-value}\\
\midrule
\rowcolor{gray!6}  M1 Petunia integrifolia - (Intercept) & 4.63 & 0.49 & 9.36 & 0.00\\
\addlinespace
M1 Petunia integrifolia - Brassica oleracea & -1.84 & 0.81 & -2.27 & 0.03\\
\addlinespace
\rowcolor{gray!6}  M1 Petunia integrifolia - Brassica rapa & -0.97 & 0.81 & -1.19 & 0.24\\
\addlinespace
M1 Petunia integrifolia - Capsicum annuum & 0.78 & 0.81 & 0.96 & 0.34\\
\addlinespace
\rowcolor{gray!6}  M1 Petunia integrifolia - Eruca vesicaria & -0.91 & 0.81 & -1.12 & 0.26\\
\addlinespace
M1 Petunia integrifolia - Ipomoea aquatica & -3.18 & 0.81 & -3.92 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M1 Petunia integrifolia - Ipomoea purpurea & -4.21 & 0.81 & -5.19 & 0.00\\
\addlinespace
M1 Petunia integrifolia - Sinapis alba & -2.99 & 0.81 & -3.69 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M1 Petunia integrifolia - Solanum lycopersicum & -2.40 & 0.81 & -2.96 & 0.00\\
\addlinespace
M1 Petunia integrifolia - Solanum melongena & -2.66 & 0.81 & -3.27 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - (Intercept) & 4.39 & 0.24 & 18.54 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Brassica oleracea & -0.47 & 0.41 & -1.14 & 0.26\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - Brassica rapa & -2.74 & 0.41 & -6.67 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Capsicum annuum & -4.39 & 0.41 & -10.71 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - Eruca vesicaria & -2.97 & 0.41 & -7.25 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Ipomoea aquatica & -4.13 & 0.41 & -10.06 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - Ipomoea purpurea & -3.80 & 0.41 & -9.27 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Petunia integrifolia & -1.82 & 0.41 & -4.44 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - Sinapis alba & -3.72 & 0.41 & -9.08 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Solanum melongena & -1.84 & 0.41 & -4.49 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - (Intercept) & 6.34 & 0.70 & 9.09 & 0.00\\
\addlinespace
M3 Solanum melongena - Brassica oleracea & -0.67 & 0.99 & -0.68 & 0.50\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - Brassica rapa & -4.33 & 0.99 & -4.39 & 0.00\\
\addlinespace
M3 Solanum melongena - Capsicum annuum & -2.33 & 0.99 & -2.36 & 0.02\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - Eruca vesicaria & -3.12 & 0.99 & -3.16 & 0.00\\
\addlinespace
M3 Solanum melongena - Ipomoea aquatica & -6.34 & 0.99 & -6.43 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - Ipomoea purpurea & -2.71 & 0.99 & -2.74 & 0.01\\
\addlinespace
M3 Solanum melongena - Petunia integrifolia & -1.43 & 0.99 & -1.45 & 0.15\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - Sinapis alba & -1.11 & 0.99 & -1.12 & 0.26\\
\addlinespace
M3 Solanum melongena - Solanum lycopersicum & -0.84 & 0.99 & -0.86 & 0.39\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - (Intercept) & 4.59 & 0.52 & 8.78 & 0.00\\
\addlinespace
M4 Capsicum annuum - Brassica oleracea & -1.80 & 0.74 & -2.43 & 0.02\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - Brassica rapa & -2.51 & 0.74 & -3.39 & 0.00\\
\addlinespace
M4 Capsicum annuum - Eruca vesicaria & -0.63 & 0.74 & -0.85 & 0.40\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - Ipomoea aquatica & -1.36 & 0.74 & -1.84 & 0.07\\
\addlinespace
M4 Capsicum annuum - Ipomoea purpurea & -4.00 & 0.74 & -5.41 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - Petunia integrifolia & -4.59 & 0.74 & -6.21 & 0.00\\
\addlinespace
M4 Capsicum annuum - Sinapis alba & -3.63 & 0.74 & -4.92 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - Solanum lycopersicum & -1.52 & 0.74 & -2.06 & 0.04\\
\addlinespace
M4 Capsicum annuum - Solanum melongena & -3.29 & 0.74 & -4.46 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - (Intercept) & 1.99 & 0.22 & 8.98 & 0.00\\
\addlinespace
M5 Brassica oleracea - Brassica rapa & -1.37 & 0.31 & -4.35 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - Capsicum annuum & -0.87 & 0.31 & -2.76 & 0.01\\
\addlinespace
M5 Brassica oleracea - Eruca vesicaria & -1.92 & 0.31 & -6.13 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - Ipomoea aquatica & -1.91 & 0.27 & -7.04 & 0.00\\
\addlinespace
M5 Brassica oleracea - Ipomoea purpurea & -1.99 & 0.31 & -6.35 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - Petunia integrifolia & -1.64 & 0.31 & -5.21 & 0.00\\
\addlinespace
M5 Brassica oleracea - Sinapis alba & -1.57 & 0.31 & -4.99 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - Solanum lycopersicum & -1.47 & 0.31 & -4.70 & 0.00\\
\addlinespace
M5 Brassica oleracea - Solanum melongena & -1.61 & 0.31 & -5.12 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - (Intercept) & 2.37 & 0.19 & 12.49 & 0.00\\
\addlinespace
M6 Brassica rapa - Brassica oleracea & -0.54 & 0.29 & -1.89 & 0.06\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - Capsicum annuum & -1.42 & 0.29 & -4.94 & 0.00\\
\addlinespace
M6 Brassica rapa - Eruca vesicaria & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - Ipomoea aquatica & -1.92 & 0.29 & -6.67 & 0.00\\
\addlinespace
M6 Brassica rapa - Ipomoea purpurea & -2.26 & 0.29 & -7.86 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - Petunia integrifolia & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
M6 Brassica rapa - Sinapis alba & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - Solanum lycopersicum & -1.88 & 0.29 & -6.55 & 0.00\\
\addlinespace
M6 Brassica rapa - Solanum melongena & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - (Intercept) & 1.34 & 0.35 & 3.80 & 0.00\\
\addlinespace
M8 Eruca sativa - Brassica oleracea & -1.34 & 0.50 & -2.69 & 0.01\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - Brassica rapa & 0.66 & 0.50 & 1.32 & 0.19\\
\addlinespace
M8 Eruca sativa - Capsicum annuum & -0.27 & 0.50 & -0.55 & 0.58\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - Ipomoea aquatica & 0.87 & 0.50 & 1.75 & 0.08\\
\addlinespace
M8 Eruca sativa - Ipomoea purpurea & -0.19 & 0.50 & -0.39 & 0.70\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - Petunia integrifolia & 0.20 & 0.50 & 0.41 & 0.68\\
\addlinespace
M8 Eruca sativa - Sinapis alba & 0.32 & 0.50 & 0.65 & 0.52\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - Solanum lycopersicum & -0.52 & 0.50 & -1.04 & 0.30\\
\addlinespace
M8 Eruca sativa - Solanum melongena & 0.54 & 0.50 & 1.09 & 0.28\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - (Intercept) & 0.82 & 0.20 & 4.05 & 0.00\\
\addlinespace
M9 Ipomoea purpurea - Brassica oleracea & 0.37 & 0.29 & 1.31 & 0.19\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - Brassica rapa & -0.41 & 0.29 & -1.43 & 0.16\\
\addlinespace
M9 Ipomoea purpurea - Capsicum annuum & -0.82 & 0.29 & -2.86 & 0.01\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - Eruca vesicaria & -0.75 & 0.29 & -2.62 & 0.01\\
\addlinespace
M9 Ipomoea purpurea - Ipomoea aquatica & 0.41 & 0.29 & 1.44 & 0.15\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - Petunia integrifolia & -0.37 & 0.29 & -1.31 & 0.19\\
\addlinespace
M9 Ipomoea purpurea - Sinapis alba & -0.33 & 0.29 & -1.14 & 0.26\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - Solanum lycopersicum & -0.82 & 0.29 & -2.86 & 0.01\\
\addlinespace
M9 Ipomoea purpurea - Solanum melongena & -0.24 & 0.29 & -0.82 & 0.41\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - (Intercept) & 0.80 & 0.09 & 9.36 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Brassica oleracea & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - Brassica rapa & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Capsicum annuum & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - Eruca vesicaria & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Ipomoea purpurea & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - Petunia integrifolia & -0.59 & 0.12 & -4.89 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Sinapis alba & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - Solanum lycopersicum & -0.69 & 0.12 & -5.70 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Solanum melongena & -0.80 & 0.12 & -6.62 & 0.00\\
\bottomrule
\end{longtable}

\endgroup{}

\clearpage

\begin{table}

\caption{\label{tab:unnamed-chunk-7}\textbf{Table S7.} Number of seeds produced with the 100\% foreign pollen treatments (N=900). From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events. In this table we show just the treatments that lead to seed production.}
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{>{\em}l>{\em}lr}
\toprule
\textbf{Recipient} & \textbf{Donor (100\% foreign pollen)} & \textbf{Seed number}\\
\midrule
\rowcolor{gray!6}  Solnamum lycopersicum & Sinapis alba & 3\\
\addlinespace
Solnamum melongena & Petunia integrifolia & 36\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & Eruca sativa & 3\\
\addlinespace
Capsicum annuum & Sinapis alba & 127\\
\addlinespace
\rowcolor{gray!6}  Brassica rapa & Brassica oleracea & 2\\
\addlinespace
Brassica rapa & Brassica oleracea & 13\\
\addlinespace
\rowcolor{gray!6}  Sinapis alba & Brassica oleracea & \vphantom{1} 7\\
\addlinespace
Sinapis alba & Brassica oleracea & 5\\
\addlinespace
\rowcolor{gray!6}  Sinapis alba & Brassica oleracea & \vphantom{1} 7\\
\addlinespace
Sinapis alba & Capsicum annuum & 1\\
\addlinespace
\rowcolor{gray!6}  Sinapis alba & Capsicum annuum & 6\\
\addlinespace
Sinapis alba & Solanum lycopersicum & 1\\
\addlinespace
\rowcolor{gray!6}  Eruca sativa & Petunia integrifolia & 2\\
\bottomrule
\multicolumn{3}{l}{\textsuperscript{} * Note: There are some specific cases that we think that hybridization did not occur and that}\\
\multicolumn{3}{l}{the recipient species were pollen contaminated, like the one of C. annuum with S. alba with 127}\\
\multicolumn{3}{l}{seeds. This seems to be the case for 5 other crosses that had very low seed production when they}\\
\multicolumn{3}{l}{were pollinated with 100\% foreign pollen with species of other family members. This represents}\\
\multicolumn{3}{l}{very few isolated cases (0.67\% of all the 100\% foreign pollen crosses conducted) and we}\\
\multicolumn{3}{l}{think that our results are not compromised by this fact.}\\
\end{tabular}}
\end{table}

\clearpage

\begin{table}

\caption{\label{tab:unnamed-chunk-8}\textbf{Table S8.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{rrl}
\toprule
\textbf{Lambda} & \textbf{P-value} & \textbf{Traits}\\
\midrule
\rowcolor{gray!6}  0.95 & 0.20 & Selfing rate\\
\addlinespace
1.00 & 0.00 & Pollen size\\
\addlinespace
\rowcolor{gray!6}  0.00 & 1.00 & Pollen anther\\
\addlinespace
0.00 & 1.00 & Ovule number\\
\addlinespace
\rowcolor{gray!6}  0.00 & 1.00 & Pollen-ovule ratio\\
\addlinespace
0.89 & 0.01 & Stigmatic area\\
\addlinespace
\rowcolor{gray!6}  0.70 & 0.05 & Stigma length\\
\addlinespace
0.77 & 0.03 & Stigma width\\
\addlinespace
\rowcolor{gray!6}  0.93 & 0.01 & Style length\\
\addlinespace
0.00 & 1.00 & Style width\\
\addlinespace
\rowcolor{gray!6}  0.47 & 0.30 & Ovary length\\
\addlinespace
0.00 & 1.00 & Ovary width\\
\addlinespace
\rowcolor{gray!6}  0.00 & 0.02 & SI index\\
\bottomrule
\end{tabular}
\end{table}

\clearpage

\begingroup\fontsize{7}{9}\selectfont
